---
title: "StackOverflowData"
output: bookdown::gitbook
date: "25-09-2018"
---

# Introduction

We are anlalyzing StackOverflow data. This is a data frame with 51392 observations and 154 variables


```{r Data, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
survey_results_public <- read_csv("survey_results_public.csv")
head(survey_results_public)
```

We want to predict the salary of a person based on variables like programming language, age, Formal Education, years of programming, years in a programming job, job satisfaction, job security or any kind of variable that could have a relation with it.

We are going to segment data per country since we see big differences between salaries just at looking to the data.

<!--Meter max mean salary y minimo -->

As we want to work on salaries we want to see the mean salary per country.

```{r ejemplo, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
mean_salary1=group_by(survey_results_public,Country)

mean_salary=summarise(mean_salary1,mean=mean(Salary,na.rm=TRUE),number=n())


top_mean_salary = top_n (mean_salary, 10)

library(ggplot2)

top_mean_salary %>%
  ggplot() +
  geom_bar(mapping= aes(x=Country, y=number), stat="identity", fill="tan1", colour="sienna3")+
  geom_point(mapping = aes(x=Country, y=mean))+
  geom_line(mapping= aes(x=Country, y =number)) +
  scale_y_continuous(sec.axis = sec_axis(~./max(top_mean_salary$number)))

```

## Including Plots

You can also embed plots, for example:


```{r pressure, echo=FALSE}
library(ggplot2)
ggplot(cars,aes(x=speed,y=dist)) + geom_point()
```
